Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-04-06 manuscript.Rmd
Updates to manuscript file.

```{r methodSummaryData, eval=TRUE}
#append.articles <- length(which(full.append.df$attributes == "article"))
#append.journals <- filter(full.append.df, attributes == "journal") %>% 
#    summarise(Unique = n_distinct(record))

unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(
        N = n())

@@

articles.final <- length(which(full.df$attributes == "article"))
journals.final <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))

@@

final.list <- cbind(n.so.yr, H)
final.list <- arrange(final.list, desc(n))
```

@@

plot.journal.count <- ggplot(n.journals.year, aes(as.factor(record.y), 
                    y = Journal.count, group=1)) + 
    geom_line(colour="black") +
    #geom_point(colour="red") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    ggtitle("B. Number of Journals by Year") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 70)) +
     annotate("rect", xmin = 2008-1989+1, xmax =  2012-1989+1, 
             ymin = 55, ymax = 70, alpha = .20, fill= "#0072B2") +
         annotate("rect", xmin = 2005-1989+1, xmax =  2007-1989+1, 
             ymin = 53, ymax = 62, alpha = .20, fill = "#0072B2")  
```

```{r plotAuthorCount, eval=TRUE}

year.df <- full.df %>%
        filter(attributes == "pubYear") %>%
        select(id = articleID, pubYear = record)

@@

plot.author.count <- ggplot(n_authors2_melted, aes(x = pubYear, y = value, group = summaryStat, colour = summaryStat)) + 
     geom_line(size = .75) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          title = element_text(size = 10), 
          legend.title=element_blank()) +
    scale_colour_manual(values=cbPalette)  +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(limits = c(0,2.5)) +
    ylab("Value") +
    xlab("Year") +
    ggtitle("Authors Per Article by Year")

```{r nsf, eval=TRUE}
nsf <- data.frame(c(rep(NA, 13), 238, 273, 304, 323, 308, 287, 338, 332, 308, 289, 280, NA), as.factor(seq(1989,2013, 1)))

growth <- c(rep("Unknown", 14), rep("Increase", 2), rep("Decrease", 3), "Increase", 
     rep("Decrease", 4), "Unknown")
nsf <- cbind(nsf, growth)

colnames(nsf) <- c("n.grads", "years", "growth")

#write.csv(nsf, file="nsf.csv")

@@

@@

@@

```{r eval=TRUE}
colnames(n.journals.year) <- c("years", "journals")
n_authors2 <- rename(n_authors2, years = ID, Avg.Authors = Average, Mdn.Authors = Median, Sd.Authors = Standard_Deviation)

@@

@@

```{r}
grid.arrange(plot.article.count, plot.journal.count, ncol=2)
```

@@

```{r}
plot.PhD
```

@@

>>>>

```{r methodSummaryData, eval=TRUE}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(
        N = n())

@@

articles.final <- length(which(full.df$attributes == "article"))
journals.final <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))
```

@@

final.list <- cbind(n.so.yr, H)
final.list <- arrange(final.list, desc(n))

```{r}
final.list.updated <- final.list %>% mutate(study.time = 
    as.numeric(last)-as.numeric(first) +1)

@@

plot.journal.count <- ggplot(n.journals.year, aes(as.factor(record.y), 
    y = Journal.count, group=1)) + 
    geom_line(colour="black") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    ggtitle("B. Number of Journals by Year") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 70)) +
    annotate("rect", xmin = 2008-1989+1, xmax =  2012-1989+1, 
    ymin = 55, ymax = 70, alpha = .20, fill= "#0072B2") +
    annotate("rect", xmin = 2005-1989+1, xmax =  2007-1989+1, 
    ymin = 53, ymax = 62, alpha = .20, fill = "#0072B2")  
```

```{r plotAuthorCount, eval=TRUE}
year.df <- full.df %>%
    filter(attributes == "pubYear") %>%
    select(id = articleID, pubYear = record)

@@

plot.author.count <- ggplot(n_authors2_melted, aes(x = pubYear, y = value, group = summaryStat, colour = summaryStat)) + 
    geom_line(size = .75) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10), 
    legend.title=element_blank()) +
    scale_colour_manual(values=cbPalette)  +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(limits = c(0,2.5)) +
    ylab("Value") +
    xlab("Year") +
    ggtitle("Authors Per Article by Year")
```

```{r nsf, eval=TRUE}
n.grads <- c(rep(NA, 13), 238, 273, 304, 323, 308, 287, 338, 332,      
    308, 289, 280, NA)
n.grads.1 <- c(rep(NA, 14), 238, 273, 304, 323, 308, 287, 338, 332, 
    308, 289, 280)
n.grads.2 <- c(rep(NA, 15), 238, 273, 304, 323, 308, 287, 338, 332, 
    308, 289)

years <- c(1989:2013)

growth <- c(rep("Unknown", 14), rep("Increase", 2), rep("Decrease", 
    3), "Increase", rep("Decrease", 4), "Unknown")

nsf <- data.frame(cbind(n.grads, n.grads.1, n.grads.2, years))
colnames(nsf) <- c("n.grads", "n.grads.1", "n.grads.2", "years")

#write.csv(nsf, file="nsf.csv")
```

@@

pages.df.melted <- reshape2::melt(pages.df, id.vars = "years")

@@

```{r pages.plot, eval=TRUE}

page.plot <- ggplot(pages.df.melted, aes(years, value, group = 
    variable, color=variable)) + 
    geom_line() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10), 
    legend.title=element_blank()) +
    scale_colour_manual(values=cbPalette)  +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(limits = c(0,16)) +
    ylab("Value") +
    xlab("Year") +
    ggtitle("Article Length by Year")
```

@@

```{r ratios}
years <- c(1989:2013)
article.grad.ratio <- articles.year.df$year.count / nsf$n.grads
article.grad.ratio.1 <- articles.year.df$year.count / nsf$n.grads.1
article.grad.ratio.2 <- articles.year.df$year.count / nsf$n.grads.2

ratio.df <- data.frame(cbind(years, article.grad.ratio, article.grad.ratio.1, article.grad.ratio.2))
colnames(ratio.df) <- c("years", "ratio", "ratio.1", "ratio.2")
ratio.df <- ratio.df[-(1:13), ]

grad.ratio.df.melted <- reshape2::melt(ratio.df, id.vars="years")

ratio.plot <- ggplot(grad.ratio.df.melted, aes(years, value, group= variable, 
    color=variable)) + geom_line() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10), 
    legend.title=element_blank()) +
    scale_colour_manual(values=cbPalette)  +
    scale_x_continuous(breaks=c(seq(2002, 2013))) +
    scale_y_continuous(limits = c(0,8)) +
    ylab("Value") +
    xlab("Year")

```{r eval=FALSE}
colnames(n.journals.year) <- c("years", "journals")
n_authors2 <- rename(n_authors2, years = ID, Avg.Authors = Average, Mdn.Authors = Median, Sd.Authors = Standard_Deviation)

@@

### Analyses

@@

```{r plotrticleCountText}
grid.arrange(plot.article.count, plot.journal.count, ncol=2)
```

@@

```{r plotPhDdegrees}
plot.PhD
ratio.plot
```

@@

```{r}
page.plot
```
